Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
intro

We describe and evaluate two approaches for synthesizing digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete solutions.

>>>>

We describe and evaluate two approaches for synthesizing digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
